---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oncraw

<!-- badges: start -->
<!-- badges: end -->

The oncraw package provides an easy-to-use tool for generating raw data domains (pre-SDTM clinical data) for oncology trials based on Case Report Forms (CRFs). 
The simulated data are designed to closely resemble real-world oncology trial data and can be used by researchers as training datasets to develop and test AI-enabled workflows for data processing and TFL automation.


## Installation

You can install the development version of oncraw from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("eric-zhang16/oncraw")
```

## Example

All you need to specify is how many patients. 
Let's say you want data generated for N=5 patients. 

```{r example,echo = TRUE}
library(oncraw)

# Generate raw domains for 5 patients 
domains <- genRaw(N=5)

# DM domain: demographic data 
dm <- domains$dm
dm

# TU domain: tumor evaluation data
tu <- domains$tu
head(tu)

# RS domain: response assessment data
rs <- domains$rs
head(rs)

# AE domain: adverse event data
ae <- domains$ae
head(ae)

# DD domain: death data (returns NULL if no deaths occurred)
dd <- domains$dd
head(dd)

# DS domain: disposition data (returns NULL if no disposition records exist)
ds <- domains$ds
head(ds)

# EX domain: exposure data
ex <- domains$ex
head(ex)
```

